\newpage
\section{Week 3}
\subsection{System of Linear Equations}
General form of a system of linear equations:
\begin{equation}
    \begin{aligned}
        a_{11}x_1 + a_{12}x_2 + \ldots + a_{1n}x_n &= b_1 \\
        a_{21}x_1 + a_{22}x_2 + \ldots + a_{2n}x_n &= b_2 \\
        \vdots \\
        a_{m1}x_1 + a_{m2}x_2 + \ldots + a_{mn}x_n &= b_m \\
    \end{aligned}
\end{equation}
\subsection{Row Operations}
\begin{itemize}
    \item \textbf{Row Interchange:} Interchange two rows.
    \item \textbf{Row Scaling:} Multiply a row by a non-zero scalar.
    \item \textbf{Row Replacement:} Replace a row by the sum of that row and a multiple of another row.
    \item \textbf{Elementary Row Operations:} Row Interchange, Row Scaling, Row Replacement.
\end{itemize}
\textbf{Example:}
\newline
Solve the following system of linear equations using row operations:
\begin{equation}
    \begin{aligned}
        x - 2y + 4z &= 16 \\
        x + 3y +  z &= 24 \\
        x +  y + 2z &= 7 \\
    \end{aligned}
\end{equation}
\textbf{Solution:}
\newline
$\begin{bmatrix}
    1 & -2 & 4 & 16 \\
    1 & 3 & 1 & 24 \\
    1 & 1 & 2 & 7 \\
\end{bmatrix}
\tilde{}
\begin{bmatrix}
    1 & -2 & 4 & 16  \\
    0 & 7 & -7 & -28 \\
    0 & 3 & -2 & -9 \\
\end{bmatrix}
\tilde{}
\begin{bmatrix}
    1 & -2 & 4  & 16 \\
    0 & 1  & -1 & -4 \\
    0 & 0  &  3 & -9 \\
\end{bmatrix}
\tilde{}
\begin{bmatrix}
    1 & -2 & 4  & 16 \\
    0 & 1  & -1 & -4 \\
    0 & 0  &  1 & 3 \\
\end{bmatrix}
\tilde{}
\begin{bmatrix}
    1 & -2 & 0  & 4 \\
    0 & 1  & 0  & -1 \\
    0 & 0  & 1  & 3 \\
\end{bmatrix}
\tilde{}
\begin{bmatrix}
    1 & 0 & 0  & 2 \\
    0 & 1 & 0  & -1 \\
    0 & 0 & 1  & 3 \\
\end{bmatrix}$
\newline
Therefore, the solution is $x = 2, y = -1, z = 3$.

\subsubsection{Definitions}
The \textbf{coefficient matrix} is the matrix of coefficients of the variables in the system of linear equations. The \textbf{augmented coefficient matrix} is the coefficient matrix with the constants on the right side of the vertical line. \newline
$\begin{bmatrix}
    1 & -2 & 4 |& 16 \\
    1 & 3 & 1 |& 24 \\
    1 & 1 & 2 |& 7 \\
\end{bmatrix}$
\newline
\newline
\textbf{Basic variables} are the variables that have a leading 1 in their column, see first and second column. \textbf{Free variables} are the variables that do not have a leading 1 in their column, see third column.\newline
$\begin{bmatrix}
    1 & 0 & 2   & 3\\
    0 & 1 & 1/4 & -5/4\\
    0 & 0 & 0   & 0\\
\end{bmatrix}$